---
title: "Trajectory analysis using Monocle3 with SpruceData"
author: "Sybil Herrera Foessel"
Date: 12 April 2023
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}

suppressPackageStartupMessages({
library(STutility)
  library(Seurat)
  library(harmony)
  library(gridExtra)
  library(pals)
  library(akima)
  library(readr)
  library(plotly)
  library(tibble)
  library(raster)
  library(dplyr)
  library(stringr)
  library(magrittr)
  library(ggplot2)
  library(imager)
  library(Matrix)
  library(cowplot)
  require(data.table)
  library(magick)
  library(grid)
  library(SeuratObject)
  library(SeuratWrappers)
  library(monocle3)
  #pacman::p_load(monocle3)
  pacman::p_load(tidyverse)
  library(patchwork)
  library(hdf5r) #STutility
  library(knitr) #STutility
  library(kableExtra) #STutility
  library(markdown)
  library(googler) #Google search for markers
})

```


#Read in Seurat rds file
```{r}

#Upload original Seurat Object, analysis on entire dataset
se <- readRDS("/home/st-analysis_home/sybil.hf/spruce_data/spruce_merged_PCA_harmony_Umap_FindNeigh_findClusters.rds")

se
```



```{r}

DimPlot(se, reduction ="umap", label= TRUE)

```

# Subset data of spots from cluster 2, 11, 5, 8.  

```{r}
# Subset data using STUtility 

Subset.lateralAll<-SubsetSTData(object = se, spots = colnames(se)[se$seurat_clusters %in% c("2", "11", "5", "8")])

Subset.lateralAll

#Save RDS file
saveRDS(Subset.lateralAll, file = "./SubsetLateralALL_13_Nov_23.rds")

#Read in RDS file
Subset.lateralAll <- readRDS("./SubsetLateralALL_13_Nov_23.rds")

  
```



# Perform Pre-trajectory Analysis  
```{r}
#SCTtransform and dimensionality reduction
Subset.lateralAll <- Subset.lateralAll %>% 
  SCTransform() %>%
  RunPCA() %>%
  RunUMAP(reduction = "pca", dims = 1:28)

#Cluster analysis without batch correction and then dimensionality #reduction
Subset.lateralAll <- Subset.lateralAll %>% 
  FindNeighbors(reduction = "pca", dims = 1:28) %>%
  FindClusters(resolution = 0.4) %>%
  RunUMAP(reduction = "pca", dims = 1:28)

#Save clusters to metadata
Subset.lateralAll$seurat_clusters_pca <- Subset.lateralAll$seurat_clusters

# Is the batch effect (Array_id)?
p1 <- DimPlot(Subset.lateralAll, group.by = "array_id", reduction = "umap")
p2 <- DimPlot(Subset.lateralAll, group.by = "seurat_clusters_pca", label = TRUE, label.size = 8, reduction = "umap")
p1
p2

#Do batch correction with harmony, cluster analysis and dimensionality #reduction
Subset.lateralAll <- RunHarmony(Subset.lateralAll, group.by.vars = "array_id", reduction = "pca", dims.use = 1:30, assay.use = "SCT", verbose = FALSE) %>%
  RunUMAP(reduction = "harmony", dims = 1:30) %>%
  FindNeighbors(reduction = "harmony", dims = 1:30) %>%
  FindClusters(resolution = 0.4)

#Save clusters_harmony to metadata
Subset.lateralAll$seurat_clusters_harmony <- Subset.lateralAll$seurat_clusters

#Visualize to see batch effect in umap after harmony 
p1 <- DimPlot(Subset.lateralAll, group.by = "array_id", reduction = "umap")

#Visualize clustering after harmony
p2 <- DimPlot(Subset.lateralAll, group.by = "seurat_clusters_harmony", label = TRUE, label.size = 8, reduction = "umap")
p1
p2

#Visualize 
p3 <- DimPlot(Subset.lateralAll, group.by = "array_id", reduction = "umap")

#Visualize to see batch effect in umap after harmony 
p4 <- DimPlot(Subset.lateralAll, group.by = "bud", reduction = "umap")

p5 <- DimPlot(Subset.lateralAll, group.by = "stage", reduction = "umap")

p6 <- DimPlot(Subset.lateralAll, group.by = "stage_timepoint", reduction = "umap")

p7 <- DimPlot(Subset.lateralAll, group.by = "timepoint", reduction = "umap")
p4
p5
p6
p7
```

# 1 Convert Seurat Object to Monocle3 cell_data_set object ------------------------
```{r}
#Convert to cds object with Monocle 3

cds.SubsetLateralAll <- as.cell_data_set(Subset.lateralAll)


# to extract cell metadata
colData(cds.SubsetLateralAll)
# to extract gene metdata
fData(cds.SubsetLateralAll)
rownames(fData(cds.SubsetLateralAll))[1:10]

# add a gene_short_name column
fData(cds.SubsetLateralAll)$gene_short_name <- rownames(fData(cds.SubsetLateralAll))

# to get counts
# counts(cds.SubsetLateralAll)

cds.SubsetLateralAll

```

# Subset: Input cluster and UMAP embedding from Seurat Object

```{r}

# Import cluster and UMAP information from Seurat to Monocle 3

# assign partitions, all cells are assigned to 1 partition
reacreate.partitionSubset <- c(rep(1,length(cds.SubsetLateralAll@colData@rownames)))
names(reacreate.partitionSubset) <- cds.SubsetLateralAll@colData@rownames
reacreate.partitionSubset <- as.factor(reacreate.partitionSubset)


cds.SubsetLateralAll@clusters$UMAP$partitions <- reacreate.partitionSubset

# Assign the cluster info 

list_clusterSubset <- Subset.lateralAll@active.ident
cds.SubsetLateralAll@clusters$UMAP$clusters <- list_clusterSubset


# Assign UMAP coordinate - cell embeddings

cds.SubsetLateralAll@int_colData@listData$reducedDims$UMAP <- Subset.lateralAll@reductions$umap@cell.embeddings

cds.SubsetLateralAll


```

# Learn trajectory graph with Monocle 3
```{r}
#Check
cds.SubsetLateralAll


# 3. Learn trajectory graph ------------------------
#We use partition = False since we imported the cluster and UMAP #information from Seurat. 

cds.SubsetLateralAll <- learn_graph(cds.SubsetLateralAll, use_partition = FALSE)


#Visualize with cluster label 
plot_cells(cds.SubsetLateralAll, color_cells_by="seurat_clusters_harmony", label_branch_points = FALSE,
label_roots = TRUE,
label_leaves = FALSE, label_cell_groups=FALSE)     

#Visualize with cluster label 
plot_cells(cds.SubsetLateralAll, color_cells_by="stage_timepoint", label_branch_points = FALSE,
label_roots = TRUE,
label_leaves = FALSE, label_cell_groups=FALSE)     


plot_cells(cds.SubsetLateralAll, color_cells_by = "phase", label_branch_points = FALSE,
           label_roots = TRUE, label_leaves = FALSE, label_cell_groups = FALSE)

#Visualize with cluster label 
plot_cells(cds.SubsetLateralAll, color_cells_by="timepoint", label_branch_points = FALSE,
label_roots = TRUE,
label_leaves = FALSE, label_cell_groups=FALSE)     

#Visualize with cluster label 
plot_cells(cds.SubsetLateralAll, color_cells_by="cluster", label_cell_groups=FALSE)    

cds.SubsetLateralAll

#plot_cells(cds.SubsetLateralAll)

cluster.namesSubset <- plot_cells(cds.SubsetLateralAll,
            color_cells_by = "cluster",
            label_groups_by_cluster = FALSE, group_label_size = 3)


cluster.namesSubset


```

# Order cells in pseudotime
```{r}
# 4. Order the cells in pseudotime 
#Here I need to state the initial time point (root nodes) of the #trajectory (initial cluster)

#Order cells, set initial point manually by graph interphase
cds.SubsetLateralAll <- order_cells(cds.SubsetLateralAll)

# Or a helper function to identify the root principal points, set rooting to cluster 8:

get_earliest_principal_nodeSubset <- function(cds.SubsetLateralAll, time_bin="8"){
  cell_ids <- which(colData(cds.SubsetLateralAll)[, "seurat_clusters_harmony"] == time_bin)
  
  closest_vertex <-
  cds.SubsetLateralAll@principal_graph_aux[["UMAP"]]$pr_graph_cell_proj_closest_vertex
  closest_vertex <- as.matrix(closest_vertex[colnames(cds.SubsetLateralAll), ])
  root_pr_nodes <-
  igraph::V(principal_graph(cds.SubsetLateralAll)[["UMAP"]])$name[as.numeric(names
  (which.max(table(closest_vertex[cell_ids,]))))]
  
  root_pr_nodes
}
cds.SubsetLateralAll <- order_cells(cds.SubsetLateralAll,root_pr_nodes=get_earliest_principal_nodeSubset(cds.SubsetLateralAll))


#Plot cells based on pseudotime
plot_cells(cds.SubsetLateralAll,
           color_cells_by = 'pseudotime',trajectory_graph_segment_size = 1.0,
           label_groups_by_cluster = FALSE,
           label_branch_points = FALSE,
           label_roots = TRUE,
           label_leaves = FALSE,
           graph_label_size = 2.5,
           )

# Create the plot with plot_cells()
Trajectory_UMAP_SublateralAll <- plot_cells(cds.SubsetLateralAll,
                                color_cells_by = 'pseudotime',
                                trajectory_graph_segment_size = 1.0,
                                label_groups_by_cluster = FALSE,
                                label_branch_points = FALSE,
                                label_roots = TRUE,
                                label_leaves = FALSE,
                                graph_label_size = 2.5,
                                  )


# Convert the DimPlot to a ggplot object
DimPlot_ggplot <- Trajectory_UMAP_SublateralAll + ggplot2::theme_minimal()

# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplot, filename = "./Trajectory_UMAP_root0_SublateralAll.pdf", width = 12, height = 8, units = "cm")  
------------
  #Change color

# Create the plot with plot_cells()
Trajectory_UMAP_SublateralAll <- plot_cells(cds.SubsetLateralAll,
                                color_cells_by = 'pseudotime',
                                trajectory_graph_segment_size = 1.0,
                                label_groups_by_cluster = FALSE,
                                label_branch_points = FALSE,
                                label_roots = TRUE,
                                label_leaves = FALSE,
                                graph_label_size = 2.5,
                              )

# Modify the color scale using scale_color_continuous
DimPlot_ggplot <- Trajectory_UMAP_SublateralAll + ggplot2::theme_minimal() +
                  ggplot2::scale_color_continuous(low = "yellow", high = "red") +
                  ggplot2::labs(color = "Pseudotime")

# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplot, filename = "./Trajectory_UMAP_root8_SublateralAll.pdf", width = 12, height = 8, units = "cm")

```

# Add pseudotime to Monocle and Seurat Object
```{r}
#Add pseudotime data in cds Monocle object
cds.SubsetLateralAll$monocle3_pseudotime <- pseudotime(cds.SubsetLateralAll)

#Add pseudotime in Seurat Object
Subset.lateralAll = AddMetaData(Subset.lateralAll, metadata = pseudotime(cds.SubsetLateralAll), col.name = "monocle3_pseudotime")


#Pseudotime for each cell stored in a data frame together with other #meta data
data.pseudoSubset <- as.data.frame(colData(cds.SubsetLateralAll))


# Extract the metadata from your Seurat object
metadata_Subset_LateralOrgansAll <- as.data.frame(Subset.lateralAll@meta.data)

write.csv(metadata_Subset_LateralOrgansAll, file = "./metadata_Subset_LateralOrgansAll.csv", col.names = TRUE, row.names = TRUE)





```

# Subset: Finding genes that change as a function of pseudotime
#Graph test (Morans I statistic test)

```{r}
# Finding genes that change as a function of pseudotime --------------------

deg_pseudoSub <- graph_test(cds.SubsetLateralAll, neighbor_graph = 'principal_graph', cores = 8)

#Filter and save to file

deg_pseudoSub <- deg_pseudoSub[deg_pseudoSub$q_value < 0.005, ]
write.csv(deg_pseudoSub, file = "./GraphTestSublateralALL.csv", col.names = TRUE, row.names = TRUE)


#Select top best based on Morans Statistics
BestMoransTest<-tibble::rownames_to_column(deg_pseudoSub) %>%
    dplyr::arrange(plyr::desc(morans_test_statistic), plyr::desc(-q_value)) %>% head(100)

ListBestMoransTest<-as.data.frame(BestMoransTest)
ListBestMoransTest
write.csv(ListBestMoransTest, file = "./ListBestMoransTest100.csv", col.names = TRUE, row.names = TRUE)


#Use a vector named PseudoGenes with several genes
#Visualize few of these genes
P<-FeaturePlot(Subset.lateralAll, features = PseudoGenes)
ggsave(P, filename = "PseudoGenes.png", dpi = 300, height = 7, width = 12)

#Select color for plot
colorsUMAP <- c("lightgrey", "#e41a1c")

#Visualize few of these genes
Umap_MA_488631<-FeaturePlot(Subset.lateralAll, cols= colorsUMAP, features = 'MA-488631g0010')
# Convert the Plot to a ggplot object
DimPlot_ggplotP <- Umap_MA_488631 + ggplot2::theme_minimal()
# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplotP, filename = "./FeaturePlot_UMAP_MA_488631_SubsetLateralAll_RED.pdf", width = 12, height = 8, units = "cm")


#Visualize few of these genes
P<-FeaturePlot(Subset.lateralAll, features = PseudoGenes)
ggsave(P, filename = "PseudoGenes.png", dpi = 300, height = 7, width = 12)

#Visualize few of these genes
Umap_MA_95995<-FeaturePlot(Subset.lateralAll, cols= colorsUMAP, features = 'MA-95995g0010')
# Convert the Plot to a ggplot object
DimPlot_ggplotP <- Umap_MA_95995 + ggplot2::theme_minimal()
# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplotP, filename = "./FeaturePlot_UMAP_MA_95995_PaDHN1_SubsetLateralAll_RED.pdf", width = 12, height = 8, units = "cm")

#Visualize few of these genes
VlnPlot_MA_95995<-VlnPlot(Subset.lateralAll, features = 'MA-95995g0010')
# Convert the Plot to a ggplot object
VlnPlot_ggplotP <- VlnPlot_MA_95995 + ggplot2::theme_minimal()
# Save the ggplot object as a PDF using ggsave
ggsave(VlnPlot_ggplotP, filename = "./VlnPlot_Cl_MA_95995_PaDHN1_SubsetLateralAll.pdf", width = 12, height = 8, units = "cm")


```

## Visualize clusters and pseudotime on tissue using Seurat-STUtility 
#Load Images
```{r}

#Create vector with images
imgs <- c("/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_B1_AugFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_B1_AugFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_B1_AugFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_C1_AugFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_C1_AugFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_C1_AugFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_D1_AugFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_D1_AugFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_D1_AugFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_C1_AugAcro1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_C1_AugAcro1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_C1_AugAcro1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_C1_AugAcro1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_D1_AugVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_D1_AugVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_D1_AugVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_D1_AugVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_D1_AugVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_D1_AugVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide5_V10F24-116_B1_AugVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide5_V10F24-116_B1_AugVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide5_V10F24-116_B1_AugVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide5_V10F24-116_B1_AugVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide5_V10F24-116_B1_AugVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_A1_AugAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_A1_AugAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_A1_AugAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_A1_AugAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_A1_OctVeg1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_A1_OctVeg1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_A1_OctVeg1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_B1_OctVeg2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_B1_OctVeg2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_B1_OctVeg2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_C1_OctAcro1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_C1_OctAcro1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_D1_OctAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide3_V19T26-078_D1_OctAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_C1_OctVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_C1_OctVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_C1_OctVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_D1_OctAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_D1_OctAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_D1_OctAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_A1_OctFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_A1_OctFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_A1_OctFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_B1_OctFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_B1_OctFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_B1_OctFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_C1_OctFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_C1_OctFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_A1_SeptFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide1_V19T26-100_A1_SeptFem1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_A1_SeptFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_A1_SeptFem2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_B1_SeptFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_B1_SeptFem3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_D1_SeptAcro1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_D1_SeptAcro1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_D1_SeptAcro1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide2_V19T26-029_D1_SeptAcro1.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_A1_SeptAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_A1_SeptAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_A1_SeptAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_A1_SeptAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_A1_SeptAcro2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_B1_SeptAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_B1_SeptAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_B1_SeptAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_B1_SeptAcro3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_C1_SeptVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_C1_SeptVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_C1_SeptVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_C1_SeptVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide4_V19T26-079_C1_SeptVeg1_2.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_B1_SeptVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_B1_SeptVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_B1_SeptVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide6_V10F24-117_B1_SeptVeg3.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg",
"/home/st-analysis_home/sybil.hf/spruce_data/images/Slide7_V10F24-109_D1_AugVeg4_SeptVeg4.jpg")

#Load the images to Staffli
Subset.lateralAll@tools$Staffli@imgs = imgs

imgs
#Load Images

Subset.lateralAll <- LoadImages(Subset.lateralAll, time.resolve = F, verbose = F)

UpdateSeuratObject(Subset.lateralAll)

# ImagePlot(Subset.lateralAll, method = "raster", type = "raw")

#Change to highest resolution
Subset.lateralAll<-SwitchResolution(Subset.lateralAll, xdim = 2000)

#Make dataframe of sampleids
sample.idsSubsetLatALL <- as.data.frame(Subset.lateralAll@tools$Staffli@imgs)

write.csv(sample.idsSubsetLatALL, file = "./Corrected_sampleIDs.csv", col.names = TRUE, row.names = TRUE)

ImagePlot(Subset.lateralAll, indices = c(1:88))

#Check the identity of the images!!
```


# Visualize Cluster and genes on tissue
```{r}

# Use vector with colors

colors.test3 <- c("#8E0152", "#8C510A","#C6DBEF","#6BAED6", "#80CDC1","#FDE0EF", "#DE77AE","#B3B3B3", "#B8E186", "#BF812D","#2171B5", "#4D9221") 
  
  
#Here I use the same colors as clusters
names(colors.test3) <- levels(Subset.lateralAll$seurat_clusters_harmony)

--------------

  # Test on one entry (your existing code)
pdf_width <- 40
pdf_height <- 7
entry_index <- 55  # Index of the entry in the 'imgs' vector
entry_name <- sub(".jpg$", "", basename(imgs[entry_index]))
output_file <- file.path(".", paste0("seurat_clusters_harmony_", entry_name, "_imgs", entry_index, ".pdf"))
Test1 = FeatureOverlay(Subset.lateralAll, features = "seurat_clusters_harmony", sampleids = entry_index, cols = colors.test3, show.sb = F, pt.alpha = 6, pt.border = F, ncols = 1, pt.size = 2.2, type = 'raw')
ggsave(Test1, filename = "./seurat_clusters_harmonyTest1.pdf", width = pdf_width, height = pdf_height, dpi = 3000)
------------------------------------------------
#Visualize UNIQUE CLUSTERS
# Get unique cluster numbers from Subset.lateralAll$seurat_clusters_harmony
unique_clusters <- unique(Subset.lateralAll$seurat_clusters_harmony)

# Iterate over unique cluster numbers
for (cluster in unique_clusters) {
  # Filter spots for the specific cluster
  spots.keep <- colnames(Subset.lateralAll)[Subset.lateralAll$seurat_clusters_harmony %in% cluster]
  
  # Check if there are spots for this cluster
  if (length(spots.keep)  %in% 0) {
    cat("No spots found for cluster:", cluster, "\n")
    next  # Skip to the next cluster if no spots are found for this cluster
  
  
  # Use your original subsetting method
  temp <- SubsetSTData(object = Subset.lateralAll, spots = spots.keep)
}
  # Modify the file path for PDF output with entry name, image number, cluster information, and entry_index of imgs
  cluster_output_file <- file.path(".", paste0("Sample_", entry_name, "_imgs", entry_index, "_Cluster", cluster, ".pdf"))

  # Your code for FeatureOverlay here
  FeatureOverlay(temp, features = "seurat_clusters_harmony", sampleids = entry_index, cols = colors.test3, show.sb = F, pt.alpha = 6, pt.border = F, ncols = 1, pt.size = 2.2, type = 'raw', label.by = "section_id")

  # Save the plot generated by FeatureOverlay as a PDF with adjusted size and DPI, using the cluster-specific output file path
  ggsave(filename = cluster_output_file, plot = cluster_plot, width = pdf_width, height = pdf_height, dpi = 3000)
}
------------------
++++++++++++++++++++++++++++++
  
##Visualize clusters on each entry  
 
# Parameters for PDF
pdf_width <- 20
pdf_height <-20

# Iterate over entry indices from 1 to 88
for (entry_index in 1:88) {
  entry_name <- sub(".jpg$", "", basename(imgs[entry_index]))
  output_file <- file.path(".", paste0("Sample_", entry_index, "_CL_SublateralOrgALL_", entry_name, ".pdf"))

  # Generate a cluster-specific plot using FeatureOverlay with custom section ID
  cluster_plot <- FeatureOverlay(
    object = Subset.lateralAll,
    features = "seurat_clusters_harmony",
    sampleids = entry_index,
    cols = colors.test3,
    show.sb = FALSE,
    pt.alpha = 6,
    pt.border = FALSE,
    ncols = 1,
    pt.size = 6.0,
    type = 'raw',
    # Set section_id directly
  )

  # Save the cluster-specific plot as a PDF
  ggsave(filename = output_file, plot = cluster_plot, width = pdf_width, height = pdf_height, dpi = 3000)
}
-------------------------------------------
#Visualize specific genes on all entries

  
# Parameters for PDF
pdf_width <- 20
pdf_height <-20

# Iterate over entry indices from 1 to 88
for (entry_index in 1:88) {
  entry_name <- sub(".jpg$", "", basename(imgs[entry_index]))
  output_file <- file.path(".", paste0("MA_10427828_Sample_", entry_index, "_CL_SublateralOrgALL_", entry_name, ".pdf"))

  # Generate a cluster-specific plot using FeatureOverlay with custom section ID
  cluster_plot <- FeatureOverlay(
    object = Subset.lateralAll,
    features = "MA-10427828g0010",
    sampleids = entry_index,
    show.sb = FALSE,
    pt.alpha = 6,
    pt.border = FALSE,
    ncols = 1,
    pt.size = 6.0,
    type = 'raw',
    # Set section_id directly
  )
  
 # Save the cluster-specific plot as a PDF
  ggsave(filename = output_file, plot = cluster_plot, width = pdf_width, height = pdf_height, dpi = 3000)
} 
------------------
###Using the same scale for all samples

# Define the marker of interest
marker_name <- "MA-10434540g0020"

# Fetch the expression values for the marker using FetchData
marker_data <- FetchData(object = Subset.lateralAll, assay = "SCT", vars = marker_name)

# Check if the marker is found in the data
if (!is.null(marker_data)) {
  # Get the overall range of the marker across all samples
  overall_min <- min(marker_data)
  overall_max <- max(marker_data)
  
  # Parameters for PDF
  pdf_width <- 20
  pdf_height <- 20

  # Iterate over entry indices from 1 to 88
  for (entry_index in 1:88) {
    entry_name <- sub(".jpg$", "", basename(imgs[entry_index]))
    output_file <- file.path(".", paste0("MA_10434540g0020_Sample_", entry_index, "_CL_SublateralOrgALL_", entry_name, ".pdf"))

    # Generate a cluster-specific plot using FeatureOverlay with custom section ID
    cluster_plot <- FeatureOverlay(
      object = Subset.lateralAll,
      features = marker_name,
      sampleids = entry_index,
      show.sb = FALSE,
      pt.alpha = 6,
      pt.border = FALSE,
      ncols = 1,
      pt.size = 6.0,
      type = 'raw',
      value.scale = c(overall_min, overall_max),
      min.cutoff = overall_min,
      max.cutoff = overall_max  # Set the same cutoff range for all PDFs
    )

    # Save the cluster-specific plot as a PDF
    ggsave(filename = output_file, plot = cluster_plot, width = pdf_width, height = pdf_height, dpi = 3000)
  }
} else {
  stop(paste("Marker", marker_name, "not found in the Seurat object. Please check the marker name."))
}

  
  
```


#Visualize pseudotime on tissue
```{r}
#Visualize in FeatureOverlay

##Visualize each cluster separately (one pdf file each)  
  
# Parameters for PDF
pdf_width <- 20
pdf_height <-20

colors.testPseudo <- c("#ffff33", "#e41a1c")

##USE SAME COLOR SCALE ON ALL IMAGES-Pdfs
  
# Find the minimum and maximum values for the "monocle3_pseudotime" feature across all clusters
min_pseudotime <- min(Subset.lateralAll$monocle3_pseudotime, na.rm = TRUE)
max_pseudotime <- max(Subset.lateralAll$monocle3_pseudotime, na.rm = TRUE)

# Iterate over entry indices from 1 to 88
for (entry_index in 1:88) {
  entry_name <- sub(".jpg$", "", basename(imgs[entry_index]))
  output_file <- file.path(".", paste0("Sample_", entry_index, "_PS_SublateralOrgALL_", entry_name, ".pdf"))

  # Generate a cluster-specific plot using FeatureOverlay with custom section ID
  cluster_plot <- FeatureOverlay(
    object = Subset.lateralAll,
    features = "monocle3_pseudotime",
    sampleids = entry_index,
    show.sb = FALSE,
    pt.alpha = 6,
    pt.border = FALSE,
    cols = colors.testPseudo,
    value.scale = c(min_pseudotime, max_pseudotime),  # Set the value.scale to the identified range
    ncols = 1,
    pt.size = 6.0,
    type = 'raw',
    # Set section_id directly
  )

  # Save the cluster-specific plot as a PDF
  ggsave(filename = output_file, plot = cluster_plot, width = pdf_width, height = pdf_height, dpi = 3000)
}
  
  
```



# Save and read in Seurat Object RDS with Monocle

```{r}
#Save RDS file
saveRDS(Subset.lateralAll, file = "./SubsetLateraALL_16May23.rds")

#Read in RDS file
Subset.lateralAll <- readRDS("./SubsetLateraALL_16May23.rds")

Subset.lateralAll

```




