---
title: "Trajectory analysis using Monocle3 with SpruceData, part 2"
author: "Sybil Herrera Foessel"
Date: 23 December 2023
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}

suppressPackageStartupMessages({
library(STutility)
  library(Seurat)
  library(harmony)
  library(gridExtra)
  library(pals)
  library(akima)
  library(readr)
  library(plotly)
  library(tibble)
  library(raster)
  library(dplyr)
  library(stringr)
  library(magrittr)
  library(ggplot2)
  library(imager)
  library(Matrix)
  library(cowplot)
  require(data.table)
  library(magick)
  library(grid)
  library(SeuratObject)
  library(SeuratWrappers)
  library(monocle3)
  #pacman::p_load(monocle3)
  pacman::p_load(tidyverse)
  library(patchwork)
  library(hdf5r) #STutility
  library(knitr) #STutility
  library(kableExtra) #STutility
  library(markdown)
  
})

```


#Read in Seurat rds file

```{r}

#Read in RDS file
Subset.lateralAll <- readRDS("./SubsetLateralALL_13_Nov_23.rds")
cds.SubsetLateralAll


```



#FindALLmarkers clusters in Seurat
```{r}

#Find markers from all clusters in Seurat
Markers.subcl <- FindAllMarkers(Subset.lateralAll, assay = "SCT", random.seed = 19)

#Filter for threshold
Markers.subcl <- Markers.subcl[Markers.subcl$p_val_adj < 0.005, ]

#Save RDS file
saveRDS(Markers.subcl, file = "./SignMarkersSubsetLateralALL30June2023.rds")

#Read in RDS file
Markers.subcl <- readRDS("./SignMarkersSubsetLateralALL30June2023.rds")

write.csv(Markers.subcl, file = "./AllMarkers.csv", col.names = TRUE, row.names = TRUE)

```

#Add unique markers column and annotate markers based on list by inner join
```{r}


# Add a new column 'marker_status' to indicate uniqueness or duplication
Markers.subcl$marker_status <- ifelse(duplicated(Markers.subcl$gene) | duplicated(Markers.subcl$gene, fromLast = TRUE),
                                      "Duplicated", "Unique")

#How many specific markers did we get per cluster
# Count the number of specific markers per cluster
Marker_count <- table(Markers.subcl$cluster)

# Print the number of specific markers per cluster
print(Marker_count)

# Order based on cluster, p_val_adj, ABSOLUTE avg_log2FC

Markers.subcl <- Markers.subcl[order(Markers.subcl$cluster, Markers.subcl$p_val_adj, -abs(Markers.subcl$avg_log2FC)), ]

# Filter for markers labeled as "unique"
unique_markers <- subset(Markers.subcl, marker_status == "Unique")

# Count the number of markers per cluster in unique_markers
marker_counts <- table(unique_markers$cluster)

# Print the marker counts per cluster
print(marker_counts)

write.csv(unique_markers, file = "./UniqueMarkersSubsetLateralALL.csv", col.names = TRUE, row.names = TRUE)


#Annotate based on marker list by inner join 

#Upload list with annotated markers from previous analysis
Buds_List<-read.csv("./Buds_clustersList.csv", header = TRUE, sep = ";")

#Correct name
colnames(Buds_List)[colnames(Buds_List) == "Gene"] <- "gene"

# Replace "MA-" with "MA_"
 Markers.subcl$gene<- gsub("MA-", "MA_", Markers.subcl$gene)


# Perform an inner join to merge based on the gene column and keep genes if not present in budsList
annotated_markers <- merge(Markers.subcl,Buds_List, by = "gene", all.x = TRUE)

# Print the merged data frame
print(annotated_markers)

write.csv(annotated_markers, file = "./annotated_MarkersSubsetLaterall.csv", col.names = TRUE, row.names = TRUE)

```

#Merge graph_test results with Annotated markers list
```{r}

#Read in annotated markers list
Annot_List<-read.csv("./AnnotatedMarkersSubLateralALLValues30June23.csv", header = TRUE, sep = ";")

# Order deg_pseudoSub based on highest values of morans_test_statistic
deg_pseudoSub_ordered <- deg_pseudoSub[order(-deg_pseudoSub$morans_test_statistic), ]

# Order deg_pseudoSub based on highest values of morans_test_statistic
deg_pseudoSub_ordered <- deg_pseudoSub[order(-deg_pseudoSub$morans_test_statistic), ]

deg_pseudoSub_ordered$gene<- gsub("MA-", "MA_", deg_pseudoSub_ordered$gene)

#Change Column name

colnames(deg_pseudoSub_ordered)[colnames(deg_pseudoSub_ordered) == "gene_short_name"] <- "gene"

# Keep only the top 100 rows
deg_pseudoSub_top100 <- deg_pseudoSub_ordered[1:100, ]

# Perform an inner join to merge based on the gene column and keep genes if not present in Annot List
deg_pseudoSub_orderedTop100Annot <- merge(deg_pseudoSub_top100, Annot_List, by = "gene", all.x = TRUE)

deg_pseudoSub_orderedTop100Annot <- deg_pseudoSub_orderedTop100Annot[order(-deg_pseudoSub_orderedTop100Annot$morans_test_statistic), ]

class(deg_pseudoSub_orderedTop100Annot$avg_log2FC)= "Numeric"
class(deg_pseudoSub_orderedTop100Annot$morans_test_statistic)= "Numeric"
class(deg_pseudoSub_orderedTop100Annot$morans_I)= "Numeric"
class(deg_pseudoSub_orderedTop100Annot$q_value)= "Numeric"
class(deg_pseudoSub_orderedTop100Annot$pct.1)= "Numeric"
class(deg_pseudoSub_orderedTop100Annot$pct.2)= "Numeric"
class(deg_pseudoSub_orderedTop100Annot$p_val_adj)= "Numeric"

# Replace commas with decimal points in the entire data frame
deg_pseudoSub_orderedTop100Annot <- data.frame(sapply(deg_pseudoSub_orderedTop100Annot, function(x) gsub(",", ".", x)))


write.csv(deg_pseudoSub_orderedTop100Annot, file = "./deg_pseudoSub_orderedTop100Annot.csv", col.names = TRUE, row.names = TRUE)


```

#HeatMap with stage_timepoint
```{r}
# Change the order of levels in the "stage_timepoint" variable
Subset.lateralAll$stage_timepoint <- factor(Subset.lateralAll$stage_timepoint, levels = c("August Vegetative", "August Acrocona", "August Female", "September Vegetative",  "September Acrocona", "September Female", "October Vegetative", "October Acrocona", "October Female"  ))

# Modify the labels for the "stage_timepoint" levels
Subset.lateralAll$stage_timepoint <- recode(
  Subset.lateralAll$stage_timepoint,
  "August Vegetative" = "AugVeg",
  "August Acrocona" = "AugAcro", 
  "August Female" = "AugFem", 
  "September Vegetative" = "SepVeg",  
  "September Acrocona" = "SepAcro", 
  "September Female" = "SepFem", 
  "October Vegetative" = "OctVeg", 
  "October Acrocona" = "OctAcro", 
  "October Female" = "OctFem"
  )
unique(Subset.lateralAll$stage_timepoint)  

Subset.lateralAll$stage_timepoint <- factor(Subset.lateralAll$stage_timepoint, levels = c(  "AugVeg", "AugAcro", "AugFem", "SepVeg", "SepAcro", "SepFem", "OctVeg", "OctAcro", "OctFem" ))

# Define the colors for the heatmap
colors.hm <- RColorBrewer::brewer.pal(11, "RdBu")

cluster6SubLat<- c("MA-104806g0010", "MA-10432788g0010", "MA-10426614g0010", "MA-24774g0010", "MA-10425897g0010", "MA-223085g0010", "MA-10434030g0010", "MA-104614g0010", "MA-10427910g0010")


# Create the heatmap with modified order of variables
Heatmap.Cluster6 <- DoHeatmap(
  object = Subset.lateralAll,
  features = cluster6SubLat,
  group.by = "stage_timepoint",
  label = TRUE,
  group.bar = TRUE,
  size = 2,
  angle = 360
) + scale_fill_gradientn(colors = colors.hm[11:1])


  Heatmap.PseudoGenes <- DoHeatmap(
  object = Subset.lateralAll,
  features = PseudoGenes,
  group.by = "stage_timepoint",
  label = TRUE,
  group.bar = TRUE,
  size = 2,
  angle = 360
) + scale_fill_gradientn(colors = colors.hm[11:1])


ggsave(Heatmap.PseudoGenes, filename = "HeatMap_Top10_Pseudogenes_perStageTimepoint.png", dpi = 300, height = 7, width = 12)

ggsave(Heatmap.Cluster6, filename = "Cluster6HeatShockSubLAll_perStageTimepoint.png", dpi = 300, height = 7, width = 12)

#Heatmap in png instead
colors.hm = RColorBrewer::brewer.pal(11, "RdBu")

Heatmap.ListGenes = DoHeatmap(object = se, features = ListGenes, group.by = "stage_timepoint", label = TRUE, group.bar = T, size = 2, angle = 360) + scale_fill_gradientn(colors = colors.hm[11:1])
ggsave(Heatmap.ListGenes, filename = "ListGenes_perStageTimepoint.png", dpi = 300, height = 7, width = 12)



```
# Heatmap TopGenes_Clusters
```{r}
#Check levels for clusters
levels(Subset.lateralAll@meta.data$seurat_clusters)

#Top 3 significant markers selected based on positive fold change per cluster
TopMarkers_Cluster<- c("MA-10425837g0010","MA-94328g0020","MA-357382g0010","MA-95995g0010","MA-10214069g0010","MA-17462g0010","MA-230716g0010","MA-3421g0010","MA-39164g0010","MA-10434303g0010","MA-125409g0010","MA-50251g0010","MA-19101g0010","MA-54204g0010","MA-591608g0010","MA-70859g0010","MA-68171g0010","MA-233898g0010","MA-3356606g0010","MA-103104g0010","MA-7016698g0010","MA-10426936g0010","MA-10307382g0050",
"MA-10317575g0030","MA-488631g0010","MA-10432569g0010","MA-31070g0010","MA-96649g0010","MA-9959066g0010","MA-105092g0010","MA-10427339g0010","MA-886307g0010","MA-120345g0010")

# Define the colors for the heatmap
colors.hm <- RColorBrewer::brewer.pal(11, "RdBu")
# Create the heatmap with modified order of variables
Heatmap_TopM_ClusterA <- DoHeatmap(
  object = Subset.lateralAll,
  features = TopMarkers_Cluster,
  group.by = "seurat_clusters",
  label = TRUE,
  group.bar = TRUE,
  size = 2,
  angle = 360
) + scale_fill_gradientn(colors = colors.hm[11:1])

Heatmap_TopM_ClusterA 
#Raster=F not to get it blurry in pdf!!!
colors.hm = RColorBrewer::brewer.pal(11, "RdBu")
Heatmap_TopM_ClusterB = DoHeatmap(object = Subset.lateralAll, features = TopMarkers_Cluster, group.by = "seurat_clusters", raster=F, label = TRUE, group.bar = T, size = 2, angle = 360) + scale_fill_gradientn(colors = colors.hm[11:1])

ggsave(Heatmap_TopM_ClusterB, filename = "HeatMap_TopMarkers_perClusterB.png", dpi = 300, height = 7, width = 12)

# Save the heatmap as a PDF using ggsave
ggsave("Heatmap_Top3M_per_Cluster_SublateralAll.pdf", plot = Heatmap_TopM_ClusterB , width = 20, height = 14, units = "cm", dpi=600)


ggsave(Heatmap_TopM_ClusterB, filename = "HeatMap_TopMarkers_perClusterB.png", dpi = 300, height = 7, width = 12)

```

#UMAP DIMPLOT to pdf
```{r}

# CLUSTERS Create a DimPlot with Seurat
DimPlot_Clusters_SubsetLateralAll <- DimPlot(object = Subset.lateralAll, reduction = "umap", group.by = "seurat_clusters", label=TRUE)

# Convert the DimPlot to a ggplot object
DimPlot_ggplot <- DimPlot_Clusters_SubsetLateralAll + ggplot2::theme_minimal()

# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplot, filename = "./DimPlot_Clusters_SubsetLateralAll.pdf", width = 12, height = 8, units = "cm")

# DIMPLOT STAGE

# Create a DimPlot with Seurat
DimPlot_Stage_SubsetLateralAll <- DimPlot(object = Subset.lateralAll, reduction = "umap", group.by = "stage")

# Convert the DimPlot to a ggplot object
DimPlot_ggplot <- DimPlot_Stage_SubsetLateralAll + ggplot2::theme_minimal()

# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplot, filename = "./DimPlot_Stage_SubsetLateralAll.pdf", width = 12, height = 8, units = "cm")


# DIMPLOT phase

# Create a DimPlot with Seurat
DimPlot_phase_SubsetLateralAll <- DimPlot(object = Subset.lateralAll, reduction = "umap", group.by = "phase")

# Convert the DimPlot to a ggplot object
DimPlot_ggplot <- DimPlot_phase_SubsetLateralAll + ggplot2::theme_minimal()

# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplot, filename = "./DimPlot_phase_SubsetLateralAll.pdf", width = 12, height = 8, units = "cm")
```


#Development PHASE stage Spruce
```{r}


# Create the vectors for each development phase
Dev_Phase1_2 <- c(10, 11, 14, 15, 16, 20, 21, 22, 23, 24, 29, 30, 31, 32)
Dev_Phase2 <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 12, 13, 25, 26, 27, 28, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85, 86, 87, 88)
Dev_Phase3 <- c(33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56)
Dev_Phase1 <- c(17, 18, 19)

# Create a vector with category names
Dev_Phase_names <- c(rep("Phase1_2", length(Dev_Phase1_2)), rep("Phase2", length(Dev_Phase2)), rep("Phase3", length(Dev_Phase3)), rep("Phase1", length(Dev_Phase1)))

# Combine all development phases into a single vector
Dev_Phase <- c(Dev_Phase1_2, Dev_Phase2, Dev_Phase3, Dev_Phase1)

# Create a dictionary as a data frame
Dev_Phase_Dict <- data.frame(Dev_Phase = Dev_Phase, Dev_Phase_Name = Dev_Phase_names)

# Reorder Dev_Phase from 1 to 88
Dev_Phase_Dict <- Dev_Phase_Dict[order(Dev_Phase_Dict$Dev_Phase), ]

# Print the reordered dictionary
Dev_Phase_Dict

# Assuming you have already created Dev_Phase_Dict as shown in your previous code

# Reorder Dev_Phase from 1 to 88 in Dev_Phase_Dict
Dev_Phase_Dict$Dev_Phase <- factor(Dev_Phase_Dict$Dev_Phase, levels = 1:88)

Phase_entry_Bud<-read.csv(file = "./Phase_entry_Bud.csv")

# Use the match function to find the corresponding Dev_Phase_corr values
match_indices <- match(Subset.lateralAll$section_id, Phase_entry_Bud$Section_id)

# Create a metadata vector with the Dev_Phase_corr values
metadata_vector <- Phase_entry_Bud$Dev_Phase_corr[match_indices]

# Use AddMetaData() to add the metadata vector to Subset.lateralAll with col.name="phase"
Subset.lateralAll = AddMetaData(Subset.lateralAll, metadata = metadata_vector, col.name = "phase")

unique(Subset.lateralAll$phase)
#Specify the order of phase levels
Subset.lateralAll$phase <- factor(Subset.lateralAll$phase, levels = c("Phase1",   "Phase1_2", "Phase2", "Phase3"))

# Now, your Subset.lateralAll object has a new metadata column "phase" based on matching "Bud"

# Count the cells in each combination of phase and stage
phase_stage_counts <- table(Subset.lateralAll$phase, Subset.lateralAll$stage)

# Display the counts
print(phase_stage_counts)

# Count the cells in each combination of phase and stage
phase_stage_timepoint_counts <- table(Subset.lateralAll$phase, Subset.lateralAll$stage_timepoint)

phase_stage_timepoint_counts

```

#Visualize genes FeaturePlot on UMAP
```{r}

PseudoGenes<- c('MA-95995g0010', 'MA-17462g0010', 'MA-488631g0010', 'MA-10214069g0010', 'MA-70859g0010', 'MA-10428408g0010', 'MA-10058549g0010', 'MA-10427828g0010', 'MA-491735g0010', 'MA-31070g0010')

P<-FeaturePlot(Subset.lateralAll, features = PseudoGenes)
ggsave(P, filename = "PseudoGenes.png", dpi = 300, height = 7, width = 12)

colorsUMAP <- c("lightgrey", "#e41a1c")

#Visualize few of these genes
Umap_MA_95995<-FeaturePlot(Subset.lateralAll, cols= colorsUMAP, features = 'MA-95995g0010')
# Convert the Plot to a ggplot object
DimPlot_ggplotP <- Umap_MA_95995 + ggplot2::theme_minimal()
# Save the ggplot object as a PDF using ggsave
ggsave(DimPlot_ggplotP, filename = "./FeaturePlot_UMAP_MA_95995_PaDHN1_SubsetLateralAll_RED.pdf", width = 12, height = 8, units = "cm")



```

# Vlnplots and BoxPlot expression againt Pseudotime value 

```{r}

# Visualize marker genes as violin plots.

P<-VlnPlot(Subset.lateralAll, features = PseudoGenes)
ggsave(P, filename = "VlnPlot_PseudoGenes.png", dpi = 300, height = 7, width = 12)


#Boxplots Cluster across Pseudotime with Clusters ordered based on Median of pseudotime 

# Calculate pseudotime and store it in a data frame
pseudotime(cds.SubsetLateralAll)
cds.SubsetLateralAll$monocle3_pseudotime <- pseudotime(cds.SubsetLateralAll)

# Pseudotime for each cell stored in a data frame together with other meta data
data.pseudo <- as.data.frame(colData(cds.SubsetLateralAll))

# Create the ggplot with a labeled y-axis, Median
ggplot(data.pseudo, aes(monocle3_pseudotime, reorder(seurat_clusters, monocle3_pseudotime, mean), fill = seurat_clusters)) +
  geom_boxplot() +
  labs(y = "Clusters (Ordered by Mean Pseudotime)", x = 'Pseudotime') +
  theme(legend.position = "none")

ggplot(data.pseudo, aes(x = monocle3_pseudotime, y = reorder(seurat_clusters, monocle3_pseudotime, mean), fill = seurat_clusters)) +
  geom_boxplot() +
  labs(y = "Seurat Clusters (Ordered by Mean Pseudotime)", x = 'Pseudotime') +
  theme(legend.position = "none", 
        axis.text.x = element_text(size = 12),  # Increase x-axis text size
        axis.text.y = element_text(size = 12))  # Increase y-axis text size



```

# Plot Gene expression of bud type against pseudotime

```{r}

#PER BUD TYPE 
#Logarithmic scale

# Assuming Subset.lateralAll is your Seurat object
data_df_Other <- data.frame(
  Pseudotime = Subset.lateralAll@meta.data$monocle3_pseudotime,
  Stage = Subset.lateralAll@meta.data$stage,
  Seurat_clusters_harmony = Subset.lateralAll@meta.data$seurat_clusters_harmony,
  MA.95995 = FetchData(object = Subset.lateralAll, assay = "SCT", vars = c("MA-95995g0010")),
  MA.488631 = FetchData(object = Subset.lateralAll, assay = "SCT", vars = c("MA-488631g0010")),
  MA.10427828 = FetchData(object = Subset.lateralAll, assay = "SCT", vars = c("MA-10427828g0010")),
  MA.211156 = FetchData(object = Subset.lateralAll, assay = "SCT", vars = c("MA-211156g0010")),
  MA.20467 = FetchData(object = Subset.lateralAll, assay = "SCT", vars = c("MA-20467g0010")),
  MA.22749g0010 = FetchData(object = Subset.lateralAll, assay = "SCT", vars = c("MA-22749g0010"))
)

# Rename columns
colnames(data_df_Other) <- gsub("MA.", "MA_", colnames(data_df_Other))

gene_names <- c("MA_95995g0010", "MA_488631g0010", "MA_10427828g0010", "MA_211156g0010", "MA_20467g0010", "MA_22749g0010")

# Loop over genes
for (gene_name in gene_names) {
  # Create a new PDF file for the gene
  pdf_filename <- paste(gene_name, "_expression_plots.pdf", sep = "")
  pdf(pdf_filename)

  # Create a new data frame for plotting
  gene_df <- data_df_Other %>%
    select(Pseudotime, Stage, gene_expression = !!sym(gene_name))

  # Specify the order of Stage levels
  gene_df$Stage <- factor(gene_df$Stage, levels = c("Veg", "Acro", "Fem"))

  # Transform the gene_expression data to logarithmic scale (e.g., base 2)
  gene_df$gene_expression <- log2(gene_df$gene_expression + 1)  # Adding 1 to avoid log(0)

  # Generate the plot with faceting
  plot <- ggplot(gene_df, aes(x = Pseudotime, y = gene_expression)) +
    geom_smooth(method = "lm", se = FALSE) +
    geom_point() +
    labs(x = "Pseudotime", y = paste("Log2(Gene Expression) -", gene_name)) +
    ggtitle(paste("Gene Expression of", gene_name, "over Pseudotime")) +
    theme(plot.title = element_text(size = 12)) + 
    facet_wrap(vars(Stage), nrow = 1, scales = "fixed")

  # Print the plot
  print(plot)

  # Close the PDF file for the gene
  dev.off()
}

```

# Plot Gene expression of bud type and timepoint against pseudotime
```{r}


# PER BUD TYPE AND TIMEPOINT
#Using logarithmic scale
#Increase text size
  
# Loop over genes
for (gene_name in gene_names) {
  # Create a new PDF file for the gene
  pdf_filename <- paste(gene_name, "_expression_plots_time.pdf", sep = "")
  pdf(pdf_filename)

  # Loop over stages
  for (stage in unique(data_df_Other$Stage)) {
    # Subset data by gene and stage
    gene_df_stage <- data_df_Other %>%
      filter(Stage == stage) %>%
      select(Timepoint, Pseudotime, gene_expression = !!sym(gene_name))
    
    # Specify the order of Timepoint levels
    gene_df_stage$Timepoint <- factor(gene_df_stage$Timepoint, levels = c("Aug", "Sept", "Oct"))
    
    # Transform the gene_expression data to logarithmic scale (e.g., base 2)
    gene_df_stage$gene_expression <- log2(gene_df_stage$gene_expression + 1)  # Adding 1 to avoid log(0)
    
    # Generate the plot with faceting by Timepoint
    plot <- ggplot(gene_df_stage, aes(x = Pseudotime, y = gene_expression)) +
      geom_smooth(method = "lm", se = FALSE) +
      geom_point() +
      labs(x = "Pseudotime", y = paste("Log2(Gene Expression)")) +
      ggtitle(paste("gene: ", gene_name, "    bud type: ", stage)) +
      theme(
        plot.title = element_text(size = 18),  # Adjust the plot title text size
        axis.title = element_text(size = 16),  # Adjust the axis title text size
        axis.text = element_text(size = 14),    # Adjust the axis text size
        strip.text = element_text(size = 16)    # Adjust the facet (Timepoint labels) text size
      ) +
      facet_wrap(vars(Timepoint), ncol = 3, scales = "fixed")
    
    # Print the plot
    print(plot)
  }

  # Close the PDF file for the gene
  dev.off()
}

  
  
```


#Table Cluster Type
```{r}
#Statistics
table(Idents(Subset.lateralAll))
table(Subset.lateralAll$stage)
prop.table(table(Idents(Subset.lateralAll)))

# Create a table of stage_timepoint per seurat_clusters_harmony
result_tableST <- table(Subset.lateralAll$seurat_clusters_harmony, Subset.lateralAll$stage_timepoint)

# Add margins to get the total count per seurat_clusters_harmony
result_table_with_totals <- addmargins(result_tableST, 2)

# Print the result_table_with_totals
print(result_table_with_totals)

-----------
# Create a table of stage_timepoint per seurat_clusters_harmony
result_tableS <- table(Subset.lateralAll$seurat_clusters_harmony, Subset.lateralAll$stage)

# Add margins to get the total count per seurat_clusters_harmony
result_table_with_totals_S <- addmargins(result_tableS, 2)

# Print the result_table_with_totals
print(result_table_with_totals_S)
-------------------------------------
# Create a table of stage_timepoint per seurat_clusters_harmony
result_tableT <- table(Subset.lateralAll$seurat_clusters_harmony, Subset.lateralAll$timepoint)

# Add margins to get the total count per seurat_clusters_harmony
result_table_with_totalsT <- addmargins(result_tableT, 2)

# Print the result_table_with_totals
print(result_table_with_totalsT)


# Create a flat table for better visualization
result_table <- ftable(Subset.lateralAll$seurat_clusters_harmony, Subset.lateralAll$stage_timepoint)
++++++++++

# Create a table of stage_timepoint per seurat_clusters_harmony
result_table <- table(Subset.lateralAll$stage_timepoint, Subset.lateralAll$seurat_clusters_harmony)

# Create a bar plot
barplot(result_table, beside = TRUE, col = rainbow(nrow(result_table)))

# Add labels and legend
legend("topright", legend = rownames(result_table), fill = rainbow(nrow(result_table)))


```



